Data Cleaning

### 2022-12-16 modeling_data/GLOBI_bee_update_clean.Rmd
update to write_csv
switching from data.table to vroom

## Read data
```{r}
library(data.table)

df <- fread( 'https://zenodo.org/record/4460654/files/interactions.csv.gz')
```

@@

# Flip target/source for above df

colnames(plant_source_df) <- as.character(lapply(colnames(plant_source_df), textclean::swap, pattern1 = 'source', pattern2 = 'target'))

plant_source_df <- plant_source_df %>% dplyr::rename(sourceCitation = targetCitation, sourceNamespace = targetNamespace, 
                                              sourceArchiveURI = targetArchiveURI, sourceDOI = targetDOI,
                                              sourceLastSeenAtUnixEpoch = targetLastSeenAtUnixEpoch)
```

## Combine
```{r}
# Combine without dropping duplicates
# The filtering method guarantees two disjoint data frames
interactions_dup = rbind(bee_source_df, plant_source_df)

# Combine and drop duplicates
interactions = rbind(bee_source_df, plant_source_df) %>% unique()
```

# Export to csv file
```{r}
write.csv(interactions_dup, "interactions_dup.csv")
```

>>>>

## Read data
```{r}
#library(data.table)
#df <- fread( 'https://zenodo.org/record/4460654/files/interactions.csv.gz')
library(vroom)
library(tidyverse)

df = vroom("all_bee_data.tsv")

```

@@

# Flip target/source for above df
colnames(plant_source_df) <- as.character(lapply(colnames(plant_source_df), textclean::swap, pattern1 = 'source', pattern2 = 'target'))
plant_source_df <- plant_source_df %>% dplyr::rename(sourceCitation = targetCitation, sourceNamespace = targetNamespace, 
                                              sourceArchiveURI = targetArchiveURI, sourceDOI = targetDOI,
                                              sourceLastSeenAtUnixEpoch = targetLastSeenAtUnixEpoch)
```

## Combine
```{r}
# Combine without dropping duplicates
# The filtering method guarantees two disjoint data frames
interactions_dup = rbind(bee_source_df, plant_source_df) 
# Combine and drop duplicates
interactions = rbind(bee_source_df, plant_source_df) %>% unique()
```

# Export to csv file
```{r}
readr::write_csv(interactions, "interactions-14dec2022.csv")
```
